\centering Syscoin 4.0: A Peer-to-Peer Electronic Cash System Built For Business Applications

### 2021-03-24 syscoin_4.0/article.tex
update

\begin{figure}[h!]
\includegraphics[width=3in]{img/current_vs_zdag.png}
\label{fig:current_vs_zdag}
\caption{Current Blockchain design vs Z-DAG} 
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[width=3in]{img/tech_stack.png}
\label{fig:tech_stack}
\caption{sys tech stack} 
\end{figure}

@@

\textbf{Table 1}

@@

\begin{figure}[h!]
\includegraphics[width=3in]{img/eth_gas_costs.png}
\label{fig:eth_gas_costs}
\caption{eth gas costs} 
\end{figure}

\begin{figure}[h!]
\includegraphics[width=3in]{img/eth_usd_density.png}
\label{fig:eth_usd_density}
\caption{eth usd density} 
\end{figure}

\begin{figure}[h!]
\includegraphics[width=3in]{img/blk_occupancy_simulations.png}
\label{fig:blk_occupancy_simulations}
\caption{sysx blk occupancy simulations} 
\end{figure}

\begin{figure}[h!]
\includegraphics[width=3in]{img/sysx_gas_costs_m1.png}
\label{fig:sysx_gas_costs_m1}
\caption{sysx gas cost simulations} 
\end{figure}

\begin{figure}[h!]
\includegraphics[width=3in]{img/sysx_usd_density.png}
\label{fig:sysx_usd_density}
\caption{sysx usd density} 
\end{figure}

\begin{figure}[h!]
\includegraphics[width=3in]{img/sysx_gas_costs_eip_1559.png}
\label{fig:sysx_gas_costs_eip_1559}
\caption{sysx gas costs eip 1559} 
\end{figure}

@@

\end{tabular}
\caption{Comparison of Gas and USD costs between ETH and SYSX}
\label{table:1}
\end{table*}

@@

\begin{figure}[h!]
\includegraphics[width=3in]{img/blk_occupancy_cost_fn.png}
\caption{BLock Occupancy Cost functions} 
\label{fig:bloc}
\end{figure}

@@

The main challenge with (\ref{eq:eip1559}) is to ensure that $b_{k}$ operates as a stationary process for states of congestion and non-congestion. A stationary process is when $b_{k}$ and $b_{k+N}$ have the same probability distributions for all N. Hence, this research problem can be broken into these two main categories. We foresee the latter problem being significantly more difficult to mathematically model than the former, as there are many non-stationary edge-cases that can arise from various attacks which have not yet been defined. For the sake of brevity, we assume $\delta_{k}$ to be a stationary Gaussian process in this discussion.

@@

\subsection{Marginal Likelihood}

@@

For this work, we looked at observations, $y$, probabilistically, which can be determined via:
\begin{equation}
p(y|x) = \int p(y | f,x) p (f, |x) df;
\end{equation}
this is otherwise known as the marginal likelihood; from a Bayesian context, this may be referred to as the evidence, which is the normalizing part of Bayes rule. Typically, due to the computational complexity, this is the tough part in Bayesian analytics, so we use Markov Chain Monte Carlo (MCMC) sampling using the PyMC3 python package.

@@

>>>>

\begin{figure}[h!]
\includegraphics[width=3in]{img/current_vs_zdag.png}
\caption{Current Blockchain design vs Z-DAG} 
\label{fig:current_vs_zdag}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[width=3in]{img/4_layer.png}
\label{fig:tech_stack}
\caption{Proposed 4-layer tech stack for Syscoin} 
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[width=3in]{img/eth_gas_costs.png}
\caption{Ethereum gas gosts in GWei from Mar 2020 to Mar 2021. The region about the observed gas costs represents the posterior distribution of $f(x*)$ given observations, $y$, for a set of dates, $x*$; see Appendix G for details}  
\label{fig:eth_gas_costs}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=3in]{img/eth_usd_density.png}
\caption{Gamma fit of Ethereum gas costs in USD using generated samples from Figure \ref{fig:eth_gas_costs} and corresponding ETHUSD prices} 
\label{fig:eth_usd_density}
\end{figure}

The results from these aforementioned estimates have been tabulated in Table \ref{table:gas_cost_estimates}; more specifically, median estimates (along with its 5th and 95th percentiles) for the costs in USD terms for both ETH and SYSX. The estimates for Ethereum were determined using historical gas costs from March 2020 to March 2021 as shown in Figure \ref{fig:eth_gas_costs}, and its distribution fit in Figure \ref{fig:eth_usd_density}.

\begin{figure}[h!]
\includegraphics[width=3in]{img/blk_occupancy_simulations.png}
\caption{Simulated block occupancies generated using methodology outlined in Appendix E; the y axis represents percentage of block occupied at given point in time. As can be seen by the gradual upward trend, this model was selected to simulate gradual growth adoption over time. } 
\label{fig:blk_occupancy_simulations}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=3in]{img/sysx_gas_costs_m1.png}
\caption{Gas cost simulations of SYSX using variant 1 of BLOC function; see Appendix E} 
\label{fig:sysx_gas_costs_m1}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=3in]{img/sysx_usd_density.png}
\caption{Gamma fit of SYSX gas cost simulations in USD using generated samples from Figure \ref{fig:sysx_gas_costs_m1} and SYSUSD prices from Mar 2020 to Mar 2021. These estimates are hypothetical, and are be subject to market price of SYS. Note that if significant adoption occurs due to future demand for cost effective alternatives, we foresee future prices being slightly higher.} 
\label{fig:sysx_usd_density}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=3in]{img/sysx_gas_costs_eip_1559.png}
\caption{Gas cost simulations of SYSX using EIP 1559; see Appendix F. We can visual see the non-stationary decline in price over time. To our knowledge, treating this non-stationary behaviour requires better understanding of the mathematical assumptions, which have not yet been analytically researched.} 
\label{fig:sysx_gas_costs_eip_1559}
\end{figure}

With regards to the SYSX cost estimates; simulated gas costs were generated using Ethereum's proposed EIP 1559 (Figure \ref{fig:sysx_gas_costs_eip_1559}) and an alternative pricing mechanism that Syscoin is currently exploring (Figure \ref{fig:sysx_gas_costs_m1}). This alternative approach is called the BLock Occupancy Cost (BLOC) function (\ref{fig:bloc}), and is driven by the occupancy of the previously generated block; see Figure \ref{fig:blk_occupancy_simulations} for simulations Appendix D for details.

\end{tabular}
\caption{Comparison of Gas and USD costs between ETH and SYSX. The confidence intervals for USD estimates were determined using historical gas costs for ETH (see Figure \ref{fig:eth_gas_costs}), and simulated gas costs for SYSX (see Figure \ref{fig:sysx_gas_costs_m1})}
\label{table:gas_cost_estimates}
\end{table*}

@@

@@

@@

\begin{figure}[h!]
\includegraphics[width=3in]{img/blk_occupancy_cost_fn.png}
\caption{BLock Occupancy Cost (BLOC) functions; model 1 and 2} 
\label{fig:bloc}
\end{figure}

@@

Ideally, we would like to see $b_{k}$ behaving as a stationary process for states of congestion and non-congestion. A stationary process is when $b_{k}$ and $b_{k+N}$ have the same probability distributions for all N. Hence, this research problem can be broken into these two main categories. We foresee the latter problem being significantly more difficult to mathematically model than the former, as there are many non-stationary edge-cases that can arise from various attacks which have not yet been defined. For the sake of brevity, we assume $\delta_{k}$ to be a stationary Gaussian process in this discussion.

@@

\section{Gaussian Processes}
\label{appendix:marginal}

@@

For this work, we looked at observations, $y$, probabilistically, which can be determined via:
\begin{equation}
p(y|x) = \int p(y | f,x) p (f, |x) df;
\end{equation}
this is otherwise known as the marginal likelihood; from a Bayesian context, this may be referred to as the evidence, which is the normalizing part of Bayes rule. The marginal likelihood can be utilized to generate conditional distribution for Gaussians to get the posterior distribution of $f(x*)$ given $y$. To do this we used Markov Chain Monte Carlo (MCMC) sampling using the PyMC3 python package; for more detail along with coding examples, see \cite{Fon20}.

@@

\bibitem{Fon20} C. Fonnesbeck, \textit{Advanced Statistical Computing, Bios 8366}, Vanderbilt University's Department of Biostatistics, Nashville, TN, May 2020, , Accessed on: Mar 2021.  [Online]. Available:  https://github.com/fonnesbeck/Bios8366/blob/master/notebooks/Section5\_1\-Gaussian-Processes.ipynb
